---
title: "Model Comparison with r4MAS - snapper-grouper complex"
output: pdf_document
toc: true
toc_depth: 3
number_sections: true
theme: united
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(vioplot)
library(scales)
```
\newpage

# Workflow
- Use the operating model (OM) from the age-structured stock assessment comparison project to simulate true population dynamics. 

  - Age-structured stock assessment comparison project OM:
  
  [https://github.com/Bai-Li-NOAA/Age_Structured_Stock_Assessment_Model_Comparison](https://github.com/Bai-Li-NOAA/Age_Structured_Stock_Assessment_Model_Comparison) 

  - R script to run the OM and Metapopulation Assessment System (MAS):
  
  [https://drive.google.com/file/d/1QevaqJ-GnEyC_ctRsa7fczC9MmKsYXAt/view?usp=sharing](https://drive.google.com/file/d/1QevaqJ-GnEyC_ctRsa7fczC9MmKsYXAt/view?usp=sharing)

- Compare MAS estimates and OM "true" values
  
  - R script: 
  
  [https://drive.google.com/file/d/1Ohvx5hnpfiiK2M8LpLOurlS_NI686T0D/view?usp=sharing](https://drive.google.com/file/d/1Ohvx5hnpfiiK2M8LpLOurlS_NI686T0D/view?usp=sharing)

  - R Markdown: 
  
  [https://drive.google.com/file/d/1Y3p5foK9uB9P7ZIiMlHaKmXVFdgfMLyV/view?usp=sharing](https://drive.google.com/file/d/1Y3p5foK9uB9P7ZIiMlHaKmXVFdgfMLyV/view?usp=sharing)

# Description of cases

- Case 1: Null case
  - $\sigma_{R} = 0.4$
  - Fishing mortality ($F$) deviations are same per iteration
  - $F$ pattern: increase
  - Selectivity pattern: simple logistic
  - Number of survey: 1
  - Initial condition: $\phi_{F} \neq \phi_{0}$

- Case 2: Increase recruitment variability
  - $\sigma_{R} = 0.6$

- Case 3: Stochastic $F$ 
  - $F$ deviations are stochastic per iteration

- Case 4: Roller coaster $F$ pattern
  - $F$ increases first and then decreases

- Case 5: Constant $F$ pattern
  - $F = F_{low}$

- Case 6: Constant $F$ pattern
  - $F = F_{MSY}$
  
- Case 7: Constant $F$ pattern
  - $F = F_{high}$

- Case 8: Selectivity pattern
  - Double logistic selectivity

- Case 9: Increase number of surveys
  - Number of survey: 2

- Case 10: Initial condition
  - $\phi_{F} = \phi_{0}$
  
- Case 11: Increase survey coefficient of variation
  - $CV_{I} = 0.5$
  
- Case 12: Misreported catch
  - Multiply "true" age composition with randomly generated values that follow a normal distribution with a mean of 50 and standard deviation of 10

Table 1. Settings of recruitment variability, fishing mortality deviations, fishing mortality patterns, selectivity patterns, and initial condition.

```{r include=FALSE}
library(dplyr)

library(knitr)
```

# Preliminary results

##  $F_{low}$ and $F_{high}$
```{r echo=FALSE, warning=FALSE, dpi=800}
# Set up working directory ------------------------------------------------

project_dir <- "C:/Users/bai.li/Documents/Github/r4MAS-model-comparison/ASSAMC_comparison/snapper_grouper/"
figure_folder_name <- "manuscript_figures"
figure_path <- file.path(project_dir, figure_folder_name)
dir.create(figure_path)

# Find Flow and Fhigh and plot yield over F figure -----------------------------------------------------
case_id <- "C1"
load(file.path(project_dir, case_id, "output", "OM", paste("OM", 1, ".RData", sep = "")))

ratio <- 0.8
msy_ratio <- ratio * max(om_output$msy$L_eq)
msy_points <- sort(abs(om_output$msy$L_eq - msy_ratio))[1:5]
f_points <- om_output$msy$f_seq[which(abs(om_output$msy$L_eq - msy_ratio) %in% msy_points)]
flow <- round(min(f_points), digits=2)
fhigh <- round(max(f_points), digits=2)

par(mar = c(4, 5, 1, 1))
plot(om_output$msy$f_seq, om_output$msy$L_eq,
     xlab = "", ylab = "",
     type = "l",
     xlim = c(0, 1), ylim = c(0, max(om_output$msy$L_eq) * 1.1),
     xaxs = "i", yaxs = "i",
     axe = F
)
axis(
  side = 1,
  at = c(0, max(om_output$msy$f_seq)),
  labels = rep(NA, 2)
)
axis(
  side = 2,
  at = c(0, max(om_output$msy$L_eq)),
  labels = rep(NA, 2)
)
lines(x = c(0, om_output$msy$Fmsy), y = c(max(om_output$msy$L_eq), max(om_output$msy$L_eq)))
lines(x = c(0, fhigh), y = c(msy_ratio, msy_ratio), lty = 2, col = "gray30")
lines(x = c(om_output$msy$Fmsy, om_output$msy$Fmsy), y = c(0, max(om_output$msy$L_eq)))
lines(x = c(flow, flow), y = c(0, msy_ratio), lty = 2, col = "gray30")
lines(x = c(fhigh, fhigh), y = c(0, msy_ratio), lty = 2, col = "gray30")
axis(1, at = c(flow, om_output$msy$Fmsy, fhigh), labels = c(expression(italic(F)[low]), expression(italic(F)[MSY]), expression(italic(F)[high])), las = 2)
axis(2, at = c(om_output$msy$msy, msy_ratio), labels = c(expression(italic(MSY)), expression(italic(0.8 * MSY))), las = 1)
```

Figure 1. The curve of the relationship of yield and fishing mortality rate ($F$) and the definitions of the lower $F$ value ($F_{low}=$ `r flow`) and higher $F$ value ($F_{high}=$ `r fhigh`) used in creation of various patterns of $F$ in the operating model. The horizontal lines indicate maximum sustainable yield ($MSY$) and 0.8*MSY*, which is 80% of $MSY$. The vertical solid line indicates the $F$ that correponds to MSY ($F_{MSY}$).   

##  Overall relative error (RE) in $SSB$, $R$, $F$, $SSB/SSB_{MSY}$, and $F/F_{MSY}$
```{r echo=FALSE, warning=FALSE, dpi=800}
# Plot SSB, R, F, SSB/SSBMSY, and F/FMSY vioplot -------------------------------------------------------
maindir_list <- paste(project_dir, case_id, sep="")

em_num <- 1

ssb_re_list <- r_re_list <- f_re_list <- ssbratio_re_list <- fratio_re_list <- list()

for(j in 1:length(maindir_list)){
  load(file.path(maindir_list[j], "output", "performance_measure.RData"))
  if (j==1){
    ssb_re <- r_re <- f_re <-
      ssbratio_re <- fratio_re <- matrix(NA, nrow=length(re_list), ncol=nrow(re_list[[1]]$ssb))
    ssb <- r <- f <- ssbratio <- fratio <- matrix(NA, nrow=length(re_list)*nrow(re_list[[1]]$ssb), ncol=em_num)
  }
  for (k in 1:em_num){
    for (i in 1:length(re_list)){
      ssb_re[i,] <- as.matrix(re_list[[i]]$ssb[,k])
      r_re[i,] <- as.matrix(re_list[[i]]$recruit[,k])
      f_re[i,] <- as.matrix(re_list[[i]]$Ftot[,k])
      ssbratio_re[i,] <- as.matrix(re_list[[i]]$ssbratio[,k])
      fratio_re[i,] <- as.matrix(re_list[[i]]$fratio[,k])
    }
    ssb[,k] <- as.vector(ssb_re)
    r[,k] <- as.vector(r_re)
    f[,k] <- as.vector(f_re)
    ssbratio[,k] <- as.vector(ssbratio_re)
    fratio[,k] <- as.vector(fratio_re)
  }
  ssb_re_list[[j]] <- ssb
  r_re_list[[j]] <- r
  f_re_list[[j]] <- f
  ssbratio_re_list[[j]] <- ssbratio
  fratio_re_list[[j]] <- fratio
}

title_var <- c(expression(italic("SSB")),
               expression(italic("R")),
               expression(italic("F")),
               expression(italic("SSB/SSB")[MSY]),
               expression(italic("F/F")[MSY]))

op<-par(no.readonly=TRUE)
par(op)
par(oma=c(5,5,0,5),mar=c(0,0,0,0.2),mfrow=c(length(case_id)+1, length(title_var)), pch=16, las=1)

ylim=c(-0.8, 0.8)
yaxis <- c(-0.4, 0, 0.4)
yaxis_label <- c(expression(paste("\u2013", "0.4")), expression("0.0"), expression("0.4"))
legend_x <- -0.2
legend_y <- 0.8

for(i in 1:length(title_var)){
  plot(NA,
       type='n',
       xlim=range(0:(em_num+1)),
       ylim=ylim,
       axes=FALSE, ann=FALSE
  )
  legend("bottomleft",
         title_var[i], 
         bty="n",
         cex=0.8)
}

for (i in 1:length(maindir_list)){
  plot(NA,
       type='n',
       xlim=range(0:(em_num+1)),
       ylim=ylim,
       axes=FALSE, ann=FALSE
  )
  axis(2, at=yaxis, labels = yaxis_label, las=2)
  vioplot(ssb_re_list[[i]][,1], add=TRUE)
  abline(h=0, col="gray30", lty=2)
  if(i == length(maindir_list)) axis(1, at=1:em_num, labels = c("MAS"), las=2, cex=0.6)
  
  legend(x=legend_x, y=legend_y, paste("C", i, sep=""), bty="n", cex=0.9)
  
  plot(NA,
       type='n',
       xlim=range(0:(em_num+1)),
       ylim=ylim,
       axes=FALSE, ann=FALSE
  )
  vioplot(r_re_list[[i]][,1], add=TRUE)
  abline(h=0, col="gray30", lty=2)
  if(i == length(maindir_list)) axis(1, at=1:em_num, labels = c("MAS"), las=2, cex=0.6)
  
  legend(x=legend_x, y=legend_y, paste("C", i, sep=""), bty="n", cex=0.9)
  
  plot(NA,
       type='n',
       xlim=range(0:(em_num+1)),
       ylim=ylim,
       axes=FALSE, ann=FALSE
  )
  vioplot(f_re_list[[i]][,1], add=TRUE)
  abline(h=0, col="gray30", lty=2)
  if(i == length(maindir_list)) axis(1, at=1:em_num, labels = c("MAS"), las=2, cex=0.6)
  legend(x=legend_x, y=legend_y, paste("C", i, sep=""), bty="n", cex=0.9)
  
  plot(NA,
       type='n',
       xlim=range(0:(em_num+1)),
       ylim=ylim,
       axes=FALSE, ann=FALSE
  )
  vioplot(ssbratio_re_list[[i]][,1], add=TRUE)
  abline(h=0, col="gray30", lty=2)
  if(i == length(maindir_list)) axis(1, at=1:em_num, labels = c("MAS"), las=2, cex=0.6)
  legend(x=legend_x, y=legend_y, paste("C", i, sep=""), bty="n", cex=0.9)
  
  plot(NA,
       type='n',
       xlim=range(0:(em_num+1)),
       ylim=ylim,
       axes=FALSE, ann=FALSE
  )
  vioplot(fratio_re_list[[i]][,1], add=TRUE)
  abline(h=0, col="gray30", lty=2)
  if(i == length(maindir_list)) axis(1, at=1:em_num, labels = c("MAS"), las=2, cex=0.6)
  legend(x=legend_x, y=legend_y, paste("C", i, sep=""), bty="n", cex=0.9)
}

par(las=2)
mtext(text="RE",side=2,line=2.5,outer=TRUE, cex=0.7)
```

Figure 2. Violin plot of relative error (RE) across years and iterations for spawning stock biomass ($SSB$), recruitment ($R$), fishing mortality rate ($F$), $SSB/SSB_{MSY}$ ($SSB/SSB$ at maximum sustainable yield [$MSY$]), and $F/F_{MSY}$ ($F/F$ at maximum sustainable yield [$MSY$]) for MAS.

```{r echo=FALSE, warning=FALSE}
# Plot SSB, R, F, SSB/SSBMSY and F/FMSY over time ------------------

## Aggregate output data
case_id <- paste("C", 1:12, sep="")
maindir_list <- paste(project_dir, case_id, sep="")

em_num <- 1

load(file.path(maindir_list[1], "output", "om_output.RData"))
ssb_median <- ssb_low <- ssb_high <-
  r_median <- r_low <- r_high <-
  f_median <- f_low <- f_high <-
  ssbratio_median <- ssbratio_low <- ssbratio_high <-
  fratio_median <- fratio_low <- fratio_high <-
  matrix(NA, nrow=nrow(om_list$ssb), ncol=(em_num+1)*length(maindir_list))

for(j in 1:length(maindir_list)){
  load(file.path(maindir_list[j], "output", "om_output.RData"))
  load(file.path(maindir_list[j], "output", "mas_output.RData"))
  data_list <- list(om_list, mas_list)
  for (k in 1:(em_num+1)){
    ssb_median[,((j-1)*(em_num+1)+k)] <- sapply(1:nrow(data_list[[k]]$ssb), function(x) boxplot.stats(data_list[[k]]$ssb[x,])$`stats`[3])
    ssb_low[,((j-1)*(em_num+1)+k)] <- sapply(1:nrow(data_list[[k]]$ssb), function(x) boxplot.stats(data_list[[k]]$ssb[x,])$`stats`[1])
    ssb_high[,((j-1)*(em_num+1)+k)] <- sapply(1:nrow(data_list[[k]]$ssb), function(x) boxplot.stats(data_list[[k]]$ssb[x,])$`stats`[5])
    
    r_median[,((j-1)*(em_num+1)+k)] <- sapply(1:nrow(data_list[[k]]$recruit), function(x) boxplot.stats(data_list[[k]]$recruit[x,])$`stats`[3])
    r_low[,((j-1)*(em_num+1)+k)] <- sapply(1:nrow(data_list[[k]]$recruit), function(x) boxplot.stats(data_list[[k]]$recruit[x,])$`stats`[1])
    r_high[,((j-1)*(em_num+1)+k)] <- sapply(1:nrow(data_list[[k]]$recruit), function(x) boxplot.stats(data_list[[k]]$recruit[x,])$`stats`[5])
    
    f_median[,((j-1)*(em_num+1)+k)] <- sapply(1:nrow(data_list[[k]]$Ftot), function(x) boxplot.stats(data_list[[k]]$Ftot[x,])$`stats`[3])
    f_low[,((j-1)*(em_num+1)+k)] <- sapply(1:nrow(data_list[[k]]$Ftot), function(x) boxplot.stats(data_list[[k]]$Ftot[x,])$`stats`[1])
    f_high[,((j-1)*(em_num+1)+k)] <- sapply(1:nrow(data_list[[k]]$Ftot), function(x) boxplot.stats(data_list[[k]]$Ftot[x,])$`stats`[5])
    
    ssbratio_median[,((j-1)*(em_num+1)+k)] <- sapply(1:nrow(data_list[[k]]$ssbratio), function(x) boxplot.stats(data_list[[k]]$ssbratio[x,])$`stats`[3])
    ssbratio_low[,((j-1)*(em_num+1)+k)] <- sapply(1:nrow(data_list[[k]]$ssbratio), function(x) boxplot.stats(data_list[[k]]$ssbratio[x,])$`stats`[1])
    ssbratio_high[,((j-1)*(em_num+1)+k)] <- sapply(1:nrow(data_list[[k]]$ssbratio), function(x) boxplot.stats(data_list[[k]]$ssbratio[x,])$`stats`[5])
    
    fratio_median[,((j-1)*(em_num+1)+k)] <- sapply(1:nrow(data_list[[k]]$fratio), function(x) boxplot.stats(data_list[[k]]$fratio[x,])$`stats`[3])
    fratio_low[,((j-1)*(em_num+1)+k)] <- sapply(1:nrow(data_list[[k]]$fratio), function(x) boxplot.stats(data_list[[k]]$fratio[x,])$`stats`[1])
    fratio_high[,((j-1)*(em_num+1)+k)] <- sapply(1:nrow(data_list[[k]]$fratio), function(x) boxplot.stats(data_list[[k]]$fratio[x,])$`stats`[5])
  }
}
```

## $SSB$ over time
```{r echo=FALSE, warning=FALSE, dpi=800}
## Plot SSB
op<-par(no.readonly=TRUE)
par(op)
par(oma=c(5,5,0,5),mar=c(0,0,0,0.2),mfrow=c(length(case_id),em_num), pch=16)

for (j in 1:length(maindir_list)){
  load(file.path(maindir_list[j], "output", "om_output.RData"))
  x_val <- om_input$year
  plot(x_val, rep(0, times=length(x_val)), ylim=range(ssb_low, ssb_high), type="l", lty=1, col="gray30", xlab="", ylab="", axes=F)
  if(j==length(maindir_list)) axis(1, at=c(5, 15, 25), labels = c(5, 15, 25))
  box()
  axis(2, at=c(3000, 7000, 11000), labels=c(3000, 7000, 11000), las=2)
  legend("topright", case_id[j], bty="n", cex=0.8)
  polygon(c(x_val, rev(x_val)), c(ssb_low[,(j-1)*(em_num+1)+1], rev(ssb_high[,(j-1)*(em_num+1)+1])), border=NA, col=alpha("gray30", 0.3))
  polygon(c(x_val, rev(x_val)), c(ssb_low[,(j-1)*(em_num+1)+2], rev(ssb_high[,(j-1)*(em_num+1)+2])), border=NA, col=alpha("deepskyblue3", 0.3))
  lines(x_val, ssb_median[,(j-1)*(em_num+1)+2], type="o", lty=1, col="deepskyblue3", pch=19, cex=0.2)
  lines(x_val, ssb_median[,(j-1)*(em_num+1)+1], type="o", lty=1, col="gray30", pch=19, cex=0.2)
  
}
mtext(text="Year",side=1,line=2.5,outer=TRUE)
mtext(text=expression(paste(italic(SSB), " (mt)")),side=2,line=3.5,outer=TRUE)

legend("top",
       legend=c("OM", "MAS"),
       col=c("gray30", "deepskyblue3"),
       fill = c("gray30", "deepskyblue3"),
       cex=0.9,
       bty="n",
       xpd=NA, 
       ncol = 2)

```

## $R$ over time
```{r echo=FALSE, warning=FALSE, dpi=800}
## R
op<-par(no.readonly=TRUE)
par(op)
par(oma=c(5,5,0,5),mar=c(0,0,0,0.2),mfrow=c(length(case_id),em_num), pch=16)

for (j in 1:length(maindir_list)){
  load(file.path(maindir_list[j], "output", "om_output.RData"))
  x_val <- om_input$year
  plot(x_val, rep(0, times=length(x_val)), ylim=range(r_low, r_high), type="l", lty=1, col="gray30", xlab="", ylab="", axes=F)
  if(j==length(maindir_list)) axis(1, at=c(5, 15, 25), labels = c(5, 15, 25))
  box()
  axis(2, at=c(800, 1600, 2400), labels=c(800, 1600, 2400), las=2)
  legend("topright", case_id[j], bty="n", cex=0.8)
  polygon(c(x_val, rev(x_val)), c(r_low[,(j-1)*(em_num+1)+1], rev(r_high[,(j-1)*(em_num+1)+1])), border=NA, col=alpha("gray30", 0.3))
  polygon(c(x_val, rev(x_val)), c(r_low[,(j-1)*(em_num+1)+2], rev(r_high[,(j-1)*(em_num+1)+2])), border=NA, col=alpha("deepskyblue3", 0.3))
  lines(x_val, r_median[,(j-1)*(em_num+1)+2], type="o", lty=1, col="deepskyblue3", pch=19, cex=0.2)
  lines(x_val, r_median[,(j-1)*(em_num+1)+1], type="o", lty=1, col="gray30", pch=19, cex=0.2)
  
}
mtext(text="Year",side=1,line=2.5,outer=TRUE)
mtext(text=expression(paste(italic(R), " (×1000 fish)")),side=2,line=3.5,outer=TRUE)

legend("top",
       legend=c("OM", "MAS"),
       col=c("gray30", "deepskyblue3"),
       fill = c("gray30", "deepskyblue3"),
       cex=0.9,
       bty="n",
       xpd=NA, 
       ncol = 2)
```

## $F$ over time
```{r echo=FALSE, warning=FALSE, dpi=800}
## F

op<-par(no.readonly=TRUE)
par(op)
par(oma=c(5,5,0,5),mar=c(0,0,0,0.2),mfrow=c(length(case_id),em_num), pch=16)

for (j in 1:length(maindir_list)){
  load(file.path(maindir_list[j], "output", "om_output.RData"))
  x_val <- om_input$year
  
  plot(x_val, rep(0, times=length(x_val)), ylim=range(f_low, f_high), type="l", lty=1, col="gray30", xlab="", ylab="", axes=F)
  if(j==length(maindir_list)) axis(1, at=c(5, 15, 25), labels = c(5, 15, 25))
  box()
  axis(2, at=c(0.2, 0.4, 0.6), labels=c(0.2, 0.4, 0.6), las=2)
  legend("topright", case_id[j], bty="n", cex=0.8)
  polygon(c(x_val, rev(x_val)), c(f_low[,(j-1)*(em_num+1)+1], rev(f_high[,(j-1)*(em_num+1)+1])), border=NA, col=alpha("gray30", 0.3))
  polygon(c(x_val, rev(x_val)), c(f_low[,(j-1)*(em_num+1)+2], rev(f_high[,(j-1)*(em_num+1)+2])), border=NA, col=alpha("deepskyblue3", 0.3))
  lines(x_val, f_median[,(j-1)*(em_num+1)+2], type="o", lty=1, col="deepskyblue3", pch=19, cex=0.2)
  lines(x_val, f_median[,(j-1)*(em_num+1)+1], type="o", lty=1, col="gray30", pch=19, cex=0.2)
}
mtext(text="Year",side=1,line=2.5,outer=TRUE)
mtext(text=expression(italic("F")),side=2,line=3.5,outer=TRUE)

legend("top",
       legend=c("OM", "MAS"),
       col=c("gray30", "deepskyblue3"),
       fill = c("gray30", "deepskyblue3"),
       cex=0.9,
       bty="n",
       xpd=NA, 
       ncol = 2)
```

## $SSB/SSB_{MSY}$ over time
```{r echo=FALSE, warning=FALSE, dpi=800}
## SSB/SSBMSY
op<-par(no.readonly=TRUE)
par(op)
par(oma=c(5,5,0,5),mar=c(0,0,0,0.2),mfrow=c(length(case_id),em_num), pch=16)

for (j in 1:length(maindir_list)){
  load(file.path(maindir_list[j], "output", "om_output.RData"))
  x_val <- om_input$year
  
  plot(x_val, rep(0, times=length(x_val)), ylim=range(ssbratio_low, ssbratio_high), type="l", lty=1, col="gray30", xlab="", ylab="", axes=F)
  if(j==length(maindir_list)) axis(1, at=c(5, 15, 25), labels = c(5, 15, 25))
  box()
  axis(2, at=c(1.5, 3, 4.5), labels=c(1.5, 3, 4.5), las=2)
  legend("topright", case_id[j], bty="n", cex=0.8)
  polygon(c(x_val, rev(x_val)), c(ssbratio_low[,(j-1)*(em_num+1)+1], rev(ssbratio_high[,(j-1)*(em_num+1)+1])), border=NA, col=alpha("gray30", 0.3))
  polygon(c(x_val, rev(x_val)), c(ssbratio_low[,(j-1)*(em_num+1)+2], rev(ssbratio_high[,(j-1)*(em_num+1)+2])), border=NA, col=alpha("deepskyblue3", 0.3))
  lines(x_val, ssbratio_median[,(j-1)*(em_num+1)+2], type="o", lty=1, col="deepskyblue3", pch=19, cex=0.2)
  lines(x_val, ssbratio_median[,(j-1)*(em_num+1)+1], type="o", lty=1, col="gray30", pch=19, cex=0.2)
  abline(h=1, col="gray", lty=2)
}
mtext(text="Year",side=1,line=2.5,outer=TRUE)
mtext(text=expression(italic(SSB/SSB)[MSY]),side=2,line=3.5,outer=TRUE)

legend("top",
       legend=c("OM", "MAS"),
       col=c("gray30", "deepskyblue3"),
       fill = c("gray30", "deepskyblue3"),
       cex=0.9,
       bty="n",
       xpd=NA, 
       ncol = 2)
```

## $F/F_{MSY}$ over time
```{r echo=FALSE, warning=FALSE, dpi=800}
## F/FMSY

op<-par(no.readonly=TRUE)
par(op)
par(oma=c(5,5,0,5),mar=c(0,0,0,0.2),mfrow=c(length(case_id),em_num), pch=16)

for (j in 1:length(maindir_list)){
  load(file.path(maindir_list[j], "output", "om_output.RData"))
  x_val <- om_input$year
  
  plot(x_val, rep(0, times=length(x_val)), ylim=range(fratio_low, fratio_high), type="l", lty=1, col="gray30", xlab="", ylab="", axes=F)
  if(j==length(maindir_list)) axis(1, at=c(5, 15, 25), labels = c(5, 15, 25))
  box()
  axis(2, at=c(0.5, 2, 3.5), labels=c(0.5, 2, 3.5), las=2)
  legend("topright", case_id[j], bty="n", cex=0.8)
  polygon(c(x_val, rev(x_val)), c(fratio_low[,(j-1)*(em_num+1)+1], rev(fratio_high[,(j-1)*(em_num+1)+1])), border=NA, col=alpha("gray30", 0.3))
  polygon(c(x_val, rev(x_val)), c(fratio_low[,(j-1)*(em_num+1)+2], rev(fratio_high[,(j-1)*(em_num+1)+2])), border=NA, col=alpha("deepskyblue3", 0.3))
  lines(x_val, fratio_median[,(j-1)*(em_num+1)+2], type="o", lty=1, col="deepskyblue3", pch=19, cex=0.2)
  lines(x_val, fratio_median[,(j-1)*(em_num+1)+1], type="o", lty=1, col="gray30", pch=19, cex=0.2)
  abline(h=1, col="gray", lty=2)
}
mtext(text="Year",side=1,line=2.5,outer=TRUE)
mtext(text=expression(italic("F/F")[MSY]),side=2,line=3.5,outer=TRUE)

legend("top",
       legend=c("OM", "MAS"),
       col=c("gray30", "deepskyblue3"),
       fill = c("gray30", "deepskyblue3"),
       cex=0.9,
       bty="n", 
       ncol = 2)

```

## Relative error in $MSY$, $F_{MSY}$ and $SSB_{MSY}$
```{r echo=FALSE, warning=FALSE, results = 'hide', dpi=800}

## Aggregate output data
maindir_list <- paste(project_dir, case_id, sep = "")

em_num <- 1

for (j in 1:length(maindir_list)) {
  load(file.path(maindir_list[j], "output", "performance_measure.RData"))
  if (j == 1) {
    msy_re <- matrix(NA, nrow = length(re_list), ncol = em_num * length(maindir_list))
    fmsy_re <- matrix(NA, nrow = length(re_list), ncol = em_num * length(maindir_list))
    ssbmsy_re <- matrix(NA, nrow = length(re_list), ncol = em_num * length(maindir_list))
  }
  for (i in 1:length(re_list)) {
    msy_re[i, ((j - 1) * em_num + 1):((j - 1) * em_num + em_num)] <- as.matrix(re_list[[i]]$msy$MAS)
    fmsy_re[i, ((j - 1) * em_num + 1):((j - 1) * em_num + em_num)] <- as.matrix(re_list[[i]]$fmsy$MAS)
    ssbmsy_re[i, ((j - 1) * em_num + 1):((j - 1) * em_num + em_num)] <- as.matrix(re_list[[i]]$ssbmsy$MAS)
  }
}

msy_stat <- matrix(NA, nrow = 3, ncol = em_num * length(maindir_list))
fmsy_stat <- matrix(NA, nrow = 3, ncol = em_num * length(maindir_list))
ssbmsy_stat <- matrix(NA, nrow = 3, ncol = em_num * length(maindir_list))

sapply(1:ncol(msy_stat), function(x) {
  msy_stat[, x] <<- boxplot.stats(msy_re[, x])$`stats`[c(1, 3, 5)]
  fmsy_stat[, x] <<- boxplot.stats(fmsy_re[, x])$`stats`[c(1, 3, 5)]
  ssbmsy_stat[, x] <<- boxplot.stats(ssbmsy_re[, x])$`stats`[c(1, 3, 5)]
})

op <- par(no.readonly = TRUE)
par(op)
par(oma = c(1, 1, 1, 1), mar = c(6, 0, 0, 0.5), mfrow = c(1, 3), pch = 16)
color <- rep("black", times = em_num)
xlim <- c(-0.6, 0.6)

plot(msy_stat[2, ], rev(1:ncol(msy_stat)),
  pch = rep(((1:em_num) + 1), times = length(maindir_list)),
  col = color,
  xlim = xlim,
  xlab = expression(paste("RE in ", italic("MSY"))), ylab = "",
  axes = F
)
segments(msy_stat[1, ], rev(1:ncol(msy_stat)), msy_stat[3, ], rev(1:ncol(msy_stat)), col = rep(color, times = length(maindir_list)))
abline(v = 0, col = "gray", lty = 2)
abline(h = seq(em_num + 0.5, ncol(msy_stat), by = em_num), col = "gray30", lty = 2)
box()
axis(1, at = seq(-0.6, 0.6, by = 0.3), labels = c(expression(paste("\u2013", "0.6")), expression(paste("\u2013", "0.3")), expression("0.0"), expression("0.6"), expression("0.3")))
text(
  x = rep(min(xlim) * 0.8, times = length(maindir_list)),
  y = seq(em_num, ncol(msy_stat), by = em_num),
  rev(case_id)
)

plot(fmsy_stat[2, ], rev(1:ncol(fmsy_stat)),
  pch = rep(((1:em_num) + 1), times = length(maindir_list)),
  col = color,
  xlim = xlim,
  xlab = expression(paste("RE in ", italic(F)[MSY])), ylab = "",
  axes = F
)
segments(fmsy_stat[1, ], rev(1:ncol(fmsy_stat)), fmsy_stat[3, ], rev(1:ncol(fmsy_stat)), col = rep(color, times = length(maindir_list)))
abline(v = 0, col = "gray", lty = 2)
abline(h = seq(em_num + 0.5, ncol(fmsy_stat), by = em_num), col = "gray30", lty = 2)
box()
axis(1, at = seq(-0.6, 0.6, by = 0.3), labels = c(expression(paste("\u2013", "0.6")), expression(paste("\u2013", "0.3")), expression("0.0"), expression("0.6"), expression("0.3")))
text(
  x = rep(min(xlim) * 0.8, times = length(maindir_list)),
  y = seq(em_num, ncol(fmsy_stat), by = em_num) ,
  rev(case_id)
)

legend(
  x = "bottom",
  inset = c(-0.2),
  legend = c("MAS"),
  pch = c(2),
  lty = c(1),
  cex = 1,
  bty = "n",
  xpd = TRUE,
  ncol = 2
)

plot(ssbmsy_stat[2, ], rev(1:ncol(ssbmsy_stat)),
  pch = rep(((1:em_num) + 1), times = length(maindir_list)),
  col = color,
  xlim = xlim,
  xlab = expression(paste("RE in ", italic(SSB)[MSY])), ylab = "",
  axes = F
)
segments(ssbmsy_stat[1, ], rev(1:ncol(ssbmsy_stat)), ssbmsy_stat[3, ], rev(1:ncol(ssbmsy_stat)), col = rep(color, times = length(maindir_list)))
abline(v = 0, col = "gray", lty = 2)
abline(h = seq(em_num + 0.5, ncol(ssbmsy_stat), by = em_num), col = "gray30", lty = 2)
box()
axis(1, at = seq(-0.6, 0.6, by = 0.3), labels = c(expression(paste("\u2013", "0.6")), expression(paste("\u2013", "0.3")), expression("0.0"), expression("0.3"), expression("0.6")))
text(
  x = rep(min(xlim) * 0.8, times = length(maindir_list)),
  y = seq(em_num, ncol(ssbmsy_stat), by = em_num),
  rev(case_id)
)

```